Persistence of marine populations under climate and fishing

### 2014-03-14 Writing/Appendix.tex
editing

\subsection{Determining stability \label{stab}}
Let $k(x)$ be a dispersal kernel describing the probability of a larva traveling a distance $x$, let $f(n)$ be the recruitment function describing the number of offspring produced by a population of size $n$, let $g(n)$ be the harvesting function describing the number of adults harvested from a population of size $n$, and let $n_t(x)$ be the number of adults at position $x$ at time $t$.  In the absence of harvesting, the integrodifference model describing the population over time is given by

@@

\subsection{MPA fluctuations}

\begin{figure}
\includegraphics[width=1\textwidth]{plots/bounded_flux.pdf}
\caption{Comparing population over time where $s = 0.1, h = 0.08$, see bounded\_flux.R for code that made this plot. }
\end{figure}

\bibliography{fish}

>>>>

\subsection{Determining stability \label{stab}}
Let $n_t(x)$ be the number of adults at position $x$ at time $t$, let $k(x)$ be a dispersal kernel describing the probability of a larva traveling a distance $x$, let $f(n)$ be the recruitment function describing the number of offspring produced by a population of size $n$, and let $g(n)$ be the harvesting function describing the number of adults harvested from a population of size $n$.  In the absence of harvesting, the integrodifference model describing the population over time is given by

@@

\pagebreak
\subsection{MPA fluctuations}

\begin{figure}[h]
\includegraphics[width=1\textwidth]{plots/bounded_flux.pdf}
\caption{Comparing population over time where $s = 0.1, h = 0.08$, see bounded\_flux.R for code that made this plot. }
\end{figure}

\pagebreak
\bibliography{fish}
